\chapter*{Acknowledgement}
\label{ch:acknowledgement}
\addcontentsline{toc}{chapter}{\nameref{ch:acknowledgement}}

First and foremost, I would like to express my sincere gratitude to my supervisors Geraint Wiggins, Steven Homer, and Nicholas Harley for their extensive guidance and unwavering support. Geraint, thank you for proposing this subject and guiding me throughout this incredible learning journey. Your constant encouragement to ask questions, even during your busy schedule, has been invaluable. Steven, thank you for introducing me to the intricate world of resonances, and Nick, I appreciate your extensive explanations of the CHAKRA framework and the insights you gave during our whiteboarding sessions to solve the problems we faced. I have been fortunate to experience an exceptionally supportive and positive research environment during the process of writing this master's thesis, for which I am immensely grateful.

I am also indebted to my dear friend Ru Chen at Chalmers University and my colleagues at ETH Zürich for providing an immersive positive intellectual influence on me and my attitude towards research. Additionally, James, I would like to thank you for always standing beside me, no matter what happens. 
Thank you for always carefully listening to my enthusiastic raves about this thesis,  the "seally" jokes for cheering me up and your thoughtful advice and feedback.

%the many memorable evenings,
%I would also like to thank my father for missing his meetings in favor of this thesis.

Lastly, I would like to express my profound gratitude to Gilles Castel. Though he is no longer with us, his lasting influence on me and other students will endure. Throughout the past years, he has been a tremendous source of inspiration, and I wish to thank him for that. The layout of this thesis includes a substantial portion of his thesis layout, serving as a tribute to his memory.



{\raggedleft \textit{Anastasia N. Krouglova} \\ \textit{19 May 2023}

}

